### 2018-03-14 Writing/Thesis/content/chapter-fundamentals.tex
Final version

A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes [Reference Missing]. The learning algorithm is then trained with one part of the data (usually the larger one), and its performance tested on the other. To get more stable results, often the process is repeated: The data is divided in k folds. Then, the learning algorithm is repeatedly trained on k-1 folds, k times, and tested on the left out subset each repetition. Results are averaged. This process is called k-fold (stratified) cross-validation [Reference Missing]. A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed [Reference Missing]. This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Monte Carlo cross-validation with a 70\%/30\% train/test split.

@@

% Definition of Kendall
The Kendall Rank Correlation Coefficient, also known as Kendall's tau, is a measure of association between two rankings of the same items \cite{kendall1938new}. For two independent random variables $X$ and $Y$ and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations. If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant. If $x_i < x_j$ but $y_i > y_j$ (or the opposite), they are viewed as discordant. Other cases are not considered. The simplest version of the statistic, called $T_A$ is then defined as

@@

To account for ties in the rankings, a second statistic, $T_B$ is defined as

>>>>

A popular approach is using a stratified split, for example splitting the data into 70\% training and 30\% test data, with the important aspect that both subsets have equal (or at least very similar) ratios of classes \cite{kohavi1995study}. The learning algorithm is then trained with one part of the data (usually the larger one), and its performance tested on the other. To get more stable results, often the process is repeated: The data is divided in k folds. Then, the learning algorithm is repeatedly trained on k-1 folds, k times, and tested on the left out subset each repetition. Results are averaged. This process is called k-fold (stratified) cross-validation \cite{kohavi1995study}. A variant of this is Monte Carlo cross-validation, where after each time the algorithm has been trained and evaluated, a new split is randomly computed \cite{xu2001monte}. This especially causes the fact that the number of folds does not dictate the ratio of the split; one could for example have 5-folds Monte Carlo cross-validation with a 70\%/30\% train/test split.

@@

% Definition of Kendall
The Kendall Rank Correlation Coefficient, also known as Kendall's tau, is a measure of association between two rankings of the same items \cite{kendall1938new}. For two independent random variables $X$ and $Y$ and observations of values $(x_1,x_2,...,x_m)$ for $X$ and $(y_1,y_2,...,y_n)$ for $Y$ with unique $x_i$ and $y_i$ respectively, the coefficient is based on comparing pairs of observations. If for two pairs $(x_i,y_i)$ and $(x_j,y_j)$ both $x_i < x_j$ and $y_i < y_j$ (or the opposite) holds, they are viewed as concordant. If $x_i < x_j$ but $y_i > y_j$ (or the opposite), they are viewed as discordant. Other cases are not considered. The simplest version of the statistic, called $T_A$ \cite{Kendall2} is then defined as

@@

To account for ties in the rankings, a second statistic, $T_B$ \cite{Kendall2} is defined as
